Everest Bio

### 2021-11-09 docs/00-ES/xar-EB-ES/xar-EB-ES.Rmd
mise à jour site

@@

# Methodology

@@

class: top left
background-image: url('figures/ES-Rec.png')
background-position: 100% 50%
background-size: 60%

## Definitions

- *Ecosystem process:*

- *Ecosystem Functions*

- *Ecosystem Services*

*- Goods and Services*:

## Ecosystem function <br> & Services

@@

@@

layout: false

@@

## Barriers and complexities

@@

# Prototyping the tool

@@

## Definitions

>The capital is not sustiable, nor reemplazable, interchangable by the financial capital of the physical capital.

.pull-left[
## Goal:
The main foal of the tool will be the identification of ES that are priorities for an industrial system inside a Territory.
]

---
## Structure of the tool

>>>>

---
include: false

@@

background-image: url('figures/ES-Rec.png')
background-position: 100% 50%
background-size: 60%

# Literature review

@@

class: top left

## Definitions
## Ecosystem function <br> & Services

- *Ecosystem process:*
- *Ecosystem Functions*
- *Ecosystem Services*
- *Goods and Services*:

@@

>The (Natural) capital is not sustiable, nor reemplazable, interchangable by the financial capital of the physical capital.

@@

layout: false
class: middle inverse

# Common International Classification of Ecosystem Services (CICES) for Integrated Environmental and Economic Accounting

@@

## CICES V5.1 Definitions

## Barriers and complexities of ES

@@

# Prototyping the tool for Everest Bio

## Goal:
The main foal of the tool will be the identification of ES that are priorities for an industrial system inside a Territory.
]

@@

## Structure of the tool

### 2021-11-09 xar-EB-general/index.Rmd
mise à jour site

class: middle, left

1. .content-box-yellow[Who am I?]
2. ERPI Laboratory
3. Green Fablab
4. Everest Bio
5. Proposition and Research axis

class: top, left
background-image: url(`r paste0(URL, 'Fabio/vosviewer/Fabio.jpg')`)
background-position: right
background-size: 70%

# Who am I?

.pull-left-1[
```{r, echo=FALSE, out.width = '60%', fig.align='center'}
knitr::include_graphics(paste0(URL, 'Fabio/Fabio.png'))
```
]

class: left middle

## My research questions so far...

class: left
background-position: 0px 75px
background-size: contain

background-image: url(`r paste0(URL, 'DRAM/DRAM-Clean-01.jpg')`)

## Are open source 3D printer good enough?

## Are open source 3D printer good enough?

Geometrical accuracy perspective

```{r , include=TRUE, echo=FALSE, fig.cap=" ", out.width = '80%', fig.align='center'}
knitr::include_graphics(paste0(URL, 'Metodologies/Master-recherche/Master-00.png'))
```

class: left
background-image: url(`r paste0(URL, 'DRAM/DRAM-Clean-02.jpg')`)
background-position: 0px 75px
background-size: contain

## Can we print recycled objects?

Recycling feasibility (Lab conditions)

class: left
background-image: url(`r paste0(URL, 'DRAM/DRAM-Clean-03.jpg')`)
background-position: 0px 75px
background-size: contain

## What about the supply chain printed recycled objects?

.pull-down[Research of Pavlo Santander. Thesis Defended Dec. 2020]

class: left
background-image: url(`r paste0(URL, 'DRAM/DRAM-05.jpeg')`)
background-position: 100px 125px
background-size: 80%

## How an innovation lab could could help as agent of change?

.footnote[
Roux-Marchand, T., Cruz, F., Dupont, L., Camargo, M., Osorio, F., 2020. Connecting the strategic intent of innovation labs and projects: the case of the Green Fablab, in: 2020 IEEE International Conference on Engineering, Technology and Innovation (ICE/ITMC). IEEE, pp. 1–10. https://doi.org/10.1109/ICE/ITMC49519.2020.9198320

Alexandre, A., Cruz Sanchez, F.A., Boudaoud, H., Camargo, M., Pearce, J.M., 2020. Mechanical Properties of Direct Waste Printing of Polylactic Acid with Universal Pellets Extruder: Comparison to Fused Filament Fabrication on Open-Source Desktop Three-Dimensional Printers. 3D Print. Addit. Manuf. 3dp.2019.0195. https://doi.org/10.1089/3dp.2019.0195
]

## What if distributed recycling could be aligned with Circular Economy priorities?

```{r, out.width = '80%', fig.align='center'}
knitr::include_graphics(paste0(URL, 'DRAM/DRAM-10.png'))
```

Cruz Sanchez, F.A., Boudaoud, H., Camargo, M., Pearce, J.M., 2020. Plastic recycling in additive manufacturing: A systematic literature review and opportunities for the circular economy. J. Clean. Prod. 264, 121602. https://doi.org/10.1016/j.jclepro.2020.121602

# However...

.left-column[
```{r, out.width = '80%', fig.align='center'}
knitr::include_graphics(paste0(URL, 'Various/Signos/attention-00.png'))
```
]

.right-column[

- Technical and economic criteria alone do not (yet) allow for informed decisions.

- Where is the environment in the techno-centrical approaches?

-  The root of the plastic waste problem needs to be addressed: the extraction and production.
-  Responsibility to act in the plastics economy

- **Adaptive injustice**: *those who find ways to adapt to changing social realities, whether forced or voluntary, are not those who are responsible for the negative changes to which they are adapting. Specifically, it is an adaptive injustice to expect communities to figure out what to do with continual flow of plastics into the economy.*

.content-box-red[**It’s time to retire this ‘privatizing profits, socializing costs’ model.**]

.footnote[
Conlon, K., 2020. Adaptive injustice: Responsibility to act in the plastics economy. Resour. Conserv. Recycl. 153, 104563. https://doi.org/10.1016/j.resconrec.2019.104563
]

@@

.pull-left[
1. Who am I?
2. .content-box-yellow[ERPI Laboratory]
3. Green Fablab
4. Everest Bio
5. Proposition and Research axis
]

@@

---
# Tool for Everest Bio

.pull-left[
## Goal:
The main foal of the tool will be the identification of ES that are priorities for an industrial system inside a Territory.
]

---
## Structure of the tool

1. Identification of the Territory
1. Two types of actors:
   1. Industrial Agent: **Identification of LCI of the Process**
   1. Territorial Agent: **Identification of the Urban ES priorities**

# CICES

1. .large.bg-yellow[Provisioning Services (biotic & Abiotic)]
1. .large.bg-yellow[Regulation & Maintenance (biotic & Abiotic)]
1. .large.bg-yellow[Cultural]

# Provisioning Services (biotic & Abiotic)
## Plants

.pull-left[
**Territorial Question**

*Are cultivated plants (Terrestrial or Aquatic) strategic for the territory for nutrition, materials or energy ?*	
]

.pull-right[
**Industrial Question**

*Are cultivated plants (Terrestrial or Aquatic) impacted in certain level by the use of your technology or proposition ?*

```{r}
library(kableExtra)
# Version Flextable
# CICES_filter <- function(ID, size = 15, ...)
# {
#   Table <- CICES %>% select(Group, Class, Code) %>% 
#   filter(Code %in% ID) %>% 
#   flextable() %>% 
#   merge_v( j = "Group") %>% 
#   fontsize(size = size,  part = "all") %>% 
#   width(width = c(2,8,1))
#   return(Table)
# }

# Version Kableextrs
CICES_filter <- function(ID, size = 15, ...)
{
  Table <- 
    CICES %>% select(Group, Class, Code, 'Example Service') %>% 
    filter(Code %in% ID) %>% 
    kbl() %>%
    #kable_paper("striped", full_width = TRUE) %>% 
    kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), font_size = size)  %>% 
  collapse_rows(columns = 1:1)

  return(Table)
}

CICES_filter(ID=c("1.1.1.1", "1.1.1.2", "1.1.1.3", 
                     "1.1.2.1", "1.1.2.2", "1.1.2.3"), size = 15)

---
# Provisioning Services (biotic & Abiotic)
## Animals

.pull-left[
**Territorial Question**

*Are Reared animals (Terrestrial or Aquatic) strategic for the territory for nutrition, materials or energy ?*	
]

.pull-right[
**Industrial Question**

*Are Reared animals (Terrestrial or Aquatic) strategic for the territory for nutrition, materials or energy ?*
]

```{r}
CICES_filter(ID=c("1.1.3.1", "1.1.3.2", "1.1.3.3", "1.1.4.1", "1.1.4.2", "1.1.4.3"), size = 15)
```

# Provisioning Services (biotic & Abiotic)
## Wild Animals & Plants

.pull-left[
**Territorial Question**

*Are Reared animals (Terrestrial or Aquatic) strategic for the territory for nutrition, materials or energy ?*	
]

.pull-right[
**Industrial Question**

*Are Reared animals (Terrestrial or Aquatic) strategic for the territory for nutrition, materials or energy ?*
]

```{r}
CICES_filter(ID=c("1.1.5.1","1.1.5.2","1.1.5.3","1.1.6.1","1.1.6.2","1.1.6.3"), size = 13)
```

---
# Provisioning Services (biotic & Abiotic)
## Genetic Material

.pull-left[
**Territorial Question**

*Is the Genetic material from plants, algae or fungi (including seed, spore or gamete production) an important element for the territory ?*	]

.pull-right[
**Industrial Question**

*Is the Genetic material from plants, algae or fungi (including seed, spore or gamete production) affected by the use of your technology int the territory ?*
]

```{r}
CICES_filter(ID=c("1.2.1.1","1.2.1.2","1.2.1.3","1.2.2.1","1.2.2.2","1.2.2.3"), size = 15)
```

# Provisioning Services (biotic & Abiotic)
## Water

.pull-left[
**Territorial Question**

*Is Water (for nutrition, materials or energy) an issue for the territory?*	]

.pull-right[
**Industrial Question**

*The is the impact of LCI?*
]

```{r ES_Provision_water}
CICES_filter(ID=c("4.2.1.1", "4.2.1.2", "4.2.1.3", "4.2.1.4", "4.2.2.1", "4.2.2.2", "4.2.2.3"
), size = 15)
```

# Provisioning Services (biotic & Abiotic)
## Others Abiotic

```{r ES_Provision_Abiotic}
#CICES_filter(ID=c("4.3.1.1","4.3.1.2","4.3.1.3","4.3.2.1","4.3.2.2","4.3.2.3","4.3.2.4","4.3.2.5","4.3.2.6"), size = 12)

CICES_filter(ID=c("4.3.1.1","4.3.1.2","4.3.1.3","4.3.2.1","4.3.2.2","4.3.2.3","4.3.2.4","4.3.2.5","4.3.2.6"), size = 15)

# CICES

1. .large.bg-yellow[Provisioning Services (biotic & Abiotic)]
1. .large.bg-yellow[Regulation & Maintenance (biotic & Abiotic)]
1. .large.bg-yellow[Cultural]

# Regulation & Maintenance (biotic & Abiotic)

## Biochemical or physical inputs to ecosystems

.pull-left[
**Territorial Question**

*Is*	]

.pull-right[
**Industrial Question**

*The *
]

```{r}
#CICES_filter(ID=c("4.3.1.1","4.3.1.2","4.3.1.3","4.3.2.1","4.3.2.2","4.3.2.3","4.3.2.4","4.3.2.5","4.3.2.6"), size = 12)

CICES_filter(ID=c("2.1.1.1", "2.1.1.2", "2.1.2.1", "2.1.2.2", "2.1.2.3"), size = 15)

# Regulation & Maintenance (biotic & Abiotic)
## Regulation of physical, chemical, biological conditions

.pull-left[
**Territorial Question**

*Is*	]

.pull-right[
**Industrial Question**

*The *
]

```{r}
#CICES_filter(ID=c("4.3.1.1","4.3.1.2","4.3.1.3","4.3.2.1","4.3.2.2","4.3.2.3","4.3.2.4","4.3.2.5","4.3.2.6"), size = 12)

CICES_filter(ID=c("2.2.1.1", "2.2.1.2", "2.2.1.3", "2.2.1.4", "2.2.1.5" ), size = 15)

# Regulation & Maintenance (biotic & Abiotic)
## Regulation of physical, chemical, biological conditions

.pull-left[
**Territorial Question**

*Is*	]

.pull-right[
**Industrial Question**

*The *
]

```{r}
#CICES_filter(ID=c("4.3.1.1","4.3.1.2","4.3.1.3","4.3.2.1","4.3.2.2","4.3.2.3","4.3.2.4","4.3.2.5","4.3.2.6"), size = 12)

CICES_filter(ID=c("2.2.2.1", "2.2.2.2", "2.2.2.3", "2.2.3.1", "2.2.3.2", "2.2.4.1", "2.2.4.2", "2.2.5.1", "2.2.5.2", "2.2.6.1", "2.2.6.2" ), size = 15)

# Regulation & Maintenance (biotic & Abiotic)
## Regulation of physical, chemical, biological conditions

.pull-left[
**Territorial Question**

*Is*	]

.pull-right[
**Industrial Question**

*The *
]

```{r}
#CICES_filter(ID=c("4.3.1.1","4.3.1.2","4.3.1.3","4.3.2.1","4.3.2.2","4.3.2.3","4.3.2.4","4.3.2.5","4.3.2.6"), size = 12)

CICES_filter(ID=c("2.2.4.1", "2.2.4.2", "2.2.5.1", "2.2.5.2", "2.2.6.1", "2.2.6.2" ), size = 15)
```

# CICES

1. .large.bg-yellow[Provisioning Services (biotic & Abiotic)]
1. .large.bg-yellow[Regulation & Maintenance (biotic & Abiotic)]
1. .large.blue[Cultural]

# Cultural (Biotic) 
## Direct contact with Nature

.pull-left[
**Territorial Question**

*Is*	]

.pull-right[
**Industrial Question**

*The *
]

```{r}
CICES_filter(ID=c("3.1.1.1", "3.1.1.2", "3.1.2.1", "3.1.2.2", "3.1.2.3", "3.1.2.4"), size = 15)
```

# Cultural (Biotic) 
## Indirect contact with Nature

.pull-left[
**Territorial Question**

*Is*	]

.pull-right[
**Industrial Question**

*The *
]

```{r}
CICES_filter(ID=c("3.2.1.1","3.2.1.2","3.2.1.3","3.2.2.1","3.2.2.2"), size = 15)

# Cultural (Abiotic) 
## Direct and Indirect link with Nature

.pull-left[
**Territorial Question**

*Is*	]

.pull-right[
**Industrial Question**

*The *
]

```{r}
CICES_filter(ID=c("6.1.1.1","6.1.2.1","6.2.1.1","6.2.2.1"), size = 15)
```

>>>>

```{r, include=FALSE}
Fabio <- TRUE
```

```{r, child= if (!Fabio) 'partials/Fabio-presentation.Rmd'}

@@

.pull-left[
1. .content-box-yellow[ERPI Laboratory]
1. Green Fablab
1. Everest Bio
1. Proposition and Research axis
]

@@
